Data Migration under a Changing Schema

### 2023-06-30 2022Migration/articleMigration.tex
WIP on chp 5 software architecture

\section{Software architecture}
   Since functionality is excluded from this paper, we discuss the software architecture of the back-end of the migration system.
   For this research, we have used the Ampersand compiler to generate the system(s).
   Figure~\ref{fig:initial} shows the starting point of the migration.
\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{figures/Before migration.png}
   \caption{Initial state of the migration}
   \label{fig:initial}
\end{figure}
   For the purpose of data migration, the existing system must make its schema available through its API.
   For this purpose, the back-end offers a service ``retrieve schema'', which provides the schema as Ampersand source-code.
   As a result, the migration engineer can rely on the schema of any generated application to be accurate.
   For this reason, we can safely assume that the schema this service provides has not been changed since it was deployed.
   Its presence allows the generator to build various front-ends and migration scripts during the lifetime of the existing system%

   After the migration engineer has produced and tested a migration script, the Ampersand compiler produces a migration system.
   It includes the schemas of both the existing system and the desired system, besides having a schema of its own.
   This is implemented by Ampersand's INCLUDE mechanism, which boils down to taking the disjoint union of the schemas.
\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{figures/During migration.png}
   \caption{During the migration}
   \label{fig:during}
\end{figure}
   Deployment of the migration system (figure~\ref{fig:during}) leaves the existing system intact.
   It enhances the system with the data set needed by the migration system, which includes the data set needed by the desired system.
   So, users will notice no difference in the existing system when the migration system is deployed.

@@

\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{figures/After migration.png}
   \caption{After the migration}
   \label{fig:after}
\end{figure}

>>>>

\section{Software architecture}
   The theory presented above roughly corresponds to the back-end of a migration system.
   This section describes its software architecture.
   For this research, we have used the Ampersand compiler to generate the system(s).
   Figure~\ref{fig:initial} shows the starting point of the migration.
\begin{figure}
   \centering
   \includegraphics[scale=0.1]{figures/Before migration.png}
   \caption{Initial state of the migration}
   \label{fig:initial}
\end{figure}
   For the purpose of data migration, the existing system must make its schema available through its API.
   For this purpose, the back-end offers a service ``retrieve schema'', which provides the schema as Ampersand source-code.
   As a result, the migration engineer can rely on the schema of any generated application to be accurate.
   For this reason, we can safely assume that the schema this service provides has not been changed since it was deployed.
   Its presence allows the generator to build various front-ends and migration scripts during the lifetime of the existing system%

   After the migration engineer has produced and tested a migration script, the Ampersand compiler produces a migration system.
   It includes the schemas of both the existing system and the desired system, besides having a schema of its own.
   This is implemented by Ampersand's INCLUDE mechanism, which boils down to taking the disjoint union of the schemas.
\begin{figure}
   \centering
   \includegraphics[scale=0.1]{figures/During migration.png}
   \caption{During the migration}
   \label{fig:during}
\end{figure}
   Deployment of the migration system (figure~\ref{fig:during}) leaves the existing system intact.
   It enhances the system with the data set needed by the migration system, which includes the data set needed by the desired system.
   So, users will notice no difference in the existing system when the migration system is deployed.

@@

\begin{figure}
   \centering
   \includegraphics[scale=0.1]{figures/After migration.png}
   \caption{After the migration}
   \label{fig:after}
\end{figure}
